Changelog

### 2021-05-24 changelog.tex
Updates from Overleaf
update

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path. I have a few choices. I can use static analysis (model checking or static program analysis). Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis. There are several papers on static side-channel analysis. But nearly all of them have high false positive rates. My personal experience with Coverity is similar. It is a commercial static program analysis tool but still has plenty of false positives.

@@

It is possible to extend the quantification part to include other side-channel signals. The key is to model the noise (e.g., Sound, CPU usages, EM signals) properly. In my dissertation, I assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information can be reliably transferred between the source (confidential data) and the destination (attackers). From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}
\item \textbf{iid assumption – does it fit your research on side-channel?}

>>>>

Abacus identifies and quantifies side-channel leakages in a single trace. So it suffers from the problem of code coverage.  That is, Abacus misses side-channel leakages in the unexecuted code path. I have a few choices. I can use static analysis (model checking or static program analysis). Although I am interested in the static analysis, I am not a big fan of current static analysis tools, especially for side-channel analysis. There are several papers on static side-channel analysis. But nearly all of them have high false positive rates. My personal experience with Coverity is similar. It is a commercial static program analysis tool but still generates plenty of false positives.

@@

It is possible to extend the quantification part to include other side-channel signals. The key is to model the noises (e.g., Sound, CPU usages, EM signals) properly. In my dissertation, I assume that an attacker can have a noise-free observation. While a noise-free observation is possible for some address-based side-channel attacks, the assumption is too ideal for many other side-channel attacks. The good news is that there are some mature methods in information theory to model the noises (e.g., Gaussian noise). The noisy-channel coding theorem provides a computable method to estimate the information can be reliably transferred between the source (confidential data) and the destination (attackers). From a research project aspect, I hope to have a stronger motivation before starting the project. 
\item \textbf{A bits vs. Q bits. Lower bounds?
       Improve the presentation
       Make the comparison more meaningful
       Etc.}
\item \textbf{iid assumption – does it fit your research on side-channel?}
